The Name of the Title is Hope

### 2023-03-07 input/2_introduction.tex

\section{Introduction}
% 1. Describe the Current Situtation
% Functions as a starting point and a common basis. Therefore it primarily contains recognizable and agreed points.
% 2. What is the complication, challenge identified
% Spells the reason for acting now. It contains threats / opportunities and the hurdles that need to be overcome.
Technological advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities as well as simplifying skill acquisition. Wearable exoskeletons move a user's body by applying forces to the extremities, for example by pulling on the fingertips (see Dexmo Haptic Glove \footnote{https://www.dextarobotics.com/}) while electrical muscle stimulation (EMS) makes the user's extremities move by sending current into the muscle activating nerves. These technologies are becoming increasingly seamless to use. However, augmented user's frequently report dissociative experiences following augmented action. They do not experience agency.

@@

% 3. Question
% Asks the question how the hurdles of the Complication can be overcome. How can we prevent the threat or seize the opportunity? Also, what would be the benefits if the complication would be overcome?
% What have others done to address this and what do we propose "instead"
In physical augmentation, this experience of agency positively impacts performance.~\citet{Kasahara2019-sk} have shown that reaction times when tapping targets on a touchscreen can be increased by augmenting the user. Critically they found an optimal increase in reaction time, \textit{pre-emptive} gain, that preserves agency. At around 80 ms preceding the naturally occurring action, user's integrate the augmentation and maintain an experience of agency. However, setting this gain factor is dependent on each specific task and requires fitting the parameters over and over again. A key question remains: How can we maintain agency during physical augmentation without training and over-fitting parameters? In other words, how can we create closed systems for users to experience natural augmentation?

% 4. (short) Answer Teaser
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
% keep this short
In this paper, we present a system that establishes a fast communication channel between the user's brain signals and a physical end effector, here EMS. The system controls the user's muscles through EMS at the time of the user's intent to interact, as measured through readiness potentials (RP) present in the user's electroencephalogram (EEG). In our user study we then applied a mixed-methods research approach to investigate whether keeping the physical impact on the user's body in line with their intention to move, preserves their sense of agency.

>>>>

\section{Introduction}
% 1. Describe the Current Situtation
% Functions as a starting point and a common basis. Therefore it primarily contains recognizable and agreed points.
% 2. What is the complication, challenge identified
% Spells the reason for acting now. It contains threats / opportunities and the hurdles that need to be overcome.
Technological advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities as well as simplifying skill acquisition. Wearable exoskeletons move a user's body by applying forces to the extremities, for example by pulling on the fingertips (see Dexmo Haptic Glove \footnote{https://www.dextarobotics.com/}) while electrical muscle stimulation (EMS) makes the user's extremities move by sending current into the muscle activating nerves. These technologies are becoming increasingly seamless to use. However, augmented user's frequently report dissociative experiences during or following augmented action. They do not experience agency.

@@

% 3. Question
% Asks the question how the hurdles of the Complication can be overcome. How can we prevent the threat or seize the opportunity? Also, what would be the benefits if the complication would be overcome?
% What have others done to address this and what do we propose "instead"
In physical augmentation, this experience of agency positively impacts performance.~\citet{Kasahara2019-sk} have shown that reaction times when tapping targets on a touchscreen can be increased by augmenting the user. Critically they found an optimal increase in reaction time, \textit{pre-emptive} gain, that preserves agency. At around 80 ms preceding the naturally occurring action, user's integrate the augmentation and maintain an experience of agency. However, setting this gain factor is dependent on each specific task and requires fitting the parameters over and over again. A key question remains: How can we maintain agency during physical augmentation without training and over-fitting parameters? In other words, how can we create closed systems for users to experience \textit{natural} augmentation?

% 4. (short) Answer Teaser
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
% keep this short
In this paper, we present a system that establishes a fast communication channel between the user's brain signals and a physical end effector, here EMS. The system controls the user's muscles through EMS at the time of the user's intent to act, as measured through readiness potentials (RP) present in the user's electroencephalogram (EEG). In our user study we then applied a mixed-methods research approach to investigate whether keeping the physical impact on the user's body in line with their intention to move, preserves their sense of agency.
